Final Project Report: Developing an AI-Assisted Grading System Using Large Language Models

### 2025-11-05 FinalProject/src/paper.tex
updatedUIData

\emph{C. Rubric Propagation \& Clipboard Interop.}
Totals update after a rubric edit; the on-screen grade table can be copied to the clipboard and pasted into an LMS/spreadsheet.  
\emph{Evidence:} a figure showing the \emph{Copy Table} UI and the pasted result (Figure~\ref{fig:copy-table}).

@@

\begin{table}[H]\centering
\caption{UI checklist for instructor workflow (presence, not preference).}\label{tab:ui-checklist}
\begin{tabularx}{\textwidth}{@{}p{6.7cm}p{1.2cm}X@{}}
\toprule
\textbf{Item} & \textbf{OK} & \textbf{Notes} \\
\midrule
Assignment creation (free-form + filled-form options) & [ ] &  \\
Template binding and identity/answer region editor (filled-form) & [ ] &  \\
Student upload flow; processing status/notifications & [ ] &  \\
Grouping view with clusters + \emph{Ungrouped} bucket & [ ] &  \\
Cluster edit tools (rename, merge, split, reassign) & [ ] &  \\
Rubric panel; apply/remove rubric items per group & [ ] &  \\
Totals update immediately after rubric edit & [ ] &  \\
Copyable grade table (\emph{Copy Table}) & [ ] &  \\
Pasted table preserves rows/columns in target app & [ ] &  \\
Audit-friendly identifiers (assignment, question, job id) visible & [ ] &  \\
\bottomrule
\end{tabularx}
\end{table}

@@

\section{UX Design Outcomes}
Report median and IQR per Likert item (1–5) and summarize key themes from free responses (readability, hierarchy, contrast, discoverability). Highlight any accessibility issues and proposed changes.

@@

\section{Summary}
Across these tests, we visually confirm end-to-end processing, vision-based semantic grouping with isolated outliers, consistent rubric propagation, and successful clipboard transfer of grades. The UI checklist verifies feature presence; the design-only UX questionnaire gauges readability and clarity; clustering metrics quantify grouping quality on a 10-student run. Crucially, the system reduces instructor workload: for this 200-answer batch, only \emph{49} manual moves were required (median \emph{2} per question), yielding an estimated \emph{$\sim$80\%} reduction in handling time versus baseline page flipping.

>>>>

\emph{C. Rubric Propagation \& Clipboard Interop.}
Totals update after a rubric edit; \emph{the rubric panel exposes a brief help tooltip clarifying positive vs.\ negative scoring semantics}; the on-screen grade table can be copied to the clipboard and pasted into an LMS/spreadsheet.
\emph{Evidence:} a figure showing the \emph{Copy Table} UI and the pasted result (Figure~\ref{fig:copy-table}).

@@

\begin{table}[H]\centering
\caption{UI checklist for instructor workflow (presence, not preference).}\label{tab:ui-checklist}
\begin{tabularx}{\textwidth}{@{}p{6.7cm}p{1.2cm}X@{}}
\toprule
\textbf{Item} & \textbf{OK} & \textbf{Notes} \\
\midrule
Assignment creation (free-form + filled-form options) & [ ] &  \\
Template binding and identity/answer region editor (filled-form) & [ ] &  \\
Student upload flow; processing status/notifications & [ ] &  \\
Grouping view with clusters + \emph{Ungrouped} bucket & [ ] &  \\
Cluster edit tools (rename, merge, split, reassign) & [ ] &  \\
Rubric panel; apply/remove rubric items per group & [ ] &  \\
Totals update immediately after rubric edit & [ ] &  \\
Copyable grade table (\emph{Copy Table}) & [ ] &  \\
Pasted table preserves rows/columns in target app & [ ] &  \\
Audit-friendly identifiers (assignment, question, job id) visible & [ ] &  \\
Job status is legible during processing (progress, last update, error/hung states) & [ ] &  \\
\bottomrule
\end{tabularx}
\end{table}

@@

\section{UX Design Outcomes}
\emph{Participants.} Four raters. One item (Q13) had a missing value; analyses use available ratings per item.

\paragraph{Central tendency and dispersion.}
Across all items, ratings were ceilinged at 5: overall mean \(=4.79\), median \(=5.0\) (Q1 \(=5.0\), Q3 \(=5.0\), IQR \(=0\)).

\paragraph{Per-item medians and IQR.}
Table~\ref{tab:likert-median-iqr} reports median and IQR per item (1–5), treating missing values as \emph{NA}. Most items show perfect consensus (IQR \(=0\)); localized dispersion appears most notably on Q14.

\begin{table}[H]\centering
\caption{Per-item medians and IQR (1–5; \emph{NA} excluded). Item labels abridge the list in \S\ref{chap:evalplan}.}
\label{tab:likert-median-iqr}
\begin{tabularx}{\textwidth}{@{}r c c X@{}}
\toprule
\textbf{Q} & \textbf{Median} & \textbf{IQR} & \textbf{Item (abridged)} \\
\midrule
1  & 5.0 & 0.0 & Layout clean/uncluttered \\
2  & 5.0 & 0.0 & Text legible / sizes appropriate \\
3  & 5.0 & 0.0 & Color/contrast readable \\
4  & 4.5 & 1.0 & Visual hierarchy / primary actions \\
5  & 5.0 & 0.5 & Labels/terminology clear \\
6  & 5.0 & 0.0 & Icons/buttons clear \\
7  & 4.5 & 1.0 & Whitespace/scanability \\
8  & 5.0 & 0.0 & Clusters visually distinguishable \\
9  & 5.0 & 0.0 & Thumbnails large/crisp \\
10 & \textbf{4.0} & 0.5 & Edit affordances easy to find \\
11 & 5.0 & 0.5 & Rubric panel easy to locate/interpret \\
12 & 5.0 & 0.0 & Score changes/totals clear \\
13 & 5.0 & 0.5 & Empty/error states understandable \\
14 & 4.5 & \textbf{1.5} & Loading/progress indicators clear \\
15 & 5.0 & 0.5 & Keyboard focus / navigation predictable \\
16 & 5.0 & 0.0 & Color not sole cue \\
17 & 5.0 & 0.0 & Overall easy to read/understand \\
\bottomrule
\end{tabularx}
\end{table}

\paragraph{Items needing attention.}
The lowest median was Q10 (\emph{Edit affordances are easy to find}) with \(\tilde{x}=4.0\) (IQR \(=0.5\)). The widest dispersion was Q14 (\emph{Loading/progress indicators are clear}) with IQR \(=1.5\), despite a high median (4.5). These indicate near-ceiling central tendency with pockets of uncertainty around (a) \emph{where/how to rename/merge/split/reassign} and (b) \emph{runtime feedback/telemetry} during processing.

\paragraph{Free-response themes (anonymized).}
\begin{itemize}
  \item \textbf{Scoring polarity help.} Missing or unclear help for negative vs.\ positive scoring semantics.
  \item \textbf{Job status clarity.} Ambiguity in whether jobs are running, complete, or hung when processing.
  \item \textbf{Selection feedback.} Highlighting the selected area in a different color was positively noted.
  \item \textbf{Demo coverage.} Some aspects were “not determinable from the video,” suggesting a documentation/demo gap.
\end{itemize}

\paragraph{Implications.}
Given the ceilinged scores, changes should target \emph{discoverability} and \emph{status legibility}, not broad visual redesign: 
(1) add an inline \emph{grading polarity} tooltip in the rubric panel; 
(2) strengthen signifiers and empty-state nudges for edit affordances (rename/merge/split/reassign); 
(3) improve job-status telemetry (progress \%, “active/hung/complete” badges, timestamped last heartbeat); 
(4) update the demo/video to explicitly show these moments so raters can verify them without inference.

@@

\section{Summary}
Across these tests, we visually confirm end-to-end processing, vision-based semantic grouping with isolated outliers, consistent rubric propagation, and successful clipboard transfer of grades. The UI checklist verifies feature presence; the design-only UX questionnaire gauges readability and clarity; clustering metrics quantify grouping quality on a 10-student run. Crucially, the system reduces instructor workload: for this 200-answer batch, only \emph{49} manual moves were required (median \emph{2} per question), yielding an estimated \emph{$\sim$80\%} reduction in handling time versus baseline page flipping.
Design-only ratings were ceilinged (median \(=5\), IQR \(=0\)) with localized uncertainty around edit-tool discoverability (Q10) and runtime status indicators (Q14), which we address via stronger signifiers, inline scoring-polarity help, and clearer job-status telemetry.
